Spectral-Spatial Hyper-spectral Image Classification Using Dual-Channel Capsule Networks

### 2020-03-11 paper/paper.tex
fixed some bugs

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{xcolor}

@@

	In this section, we introduce our proposed algorithm.
	We first described how we pre-process the HSI data, then we \textbf{depicted} the network structure and finally we
	introduced how to train the network.

@@

	Usually, a HSI dataset has labeled and unlabeled pixels.
	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
	and the rest of the labeled pixels was used to validate the model.

@@

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{subfiles}

@@

	In this section, we introduce our proposed algorithm.
	We first described how we pre-process the HSI data, then we introduced the network structure and finally we
	introduced the hyper parameters we adopted to train the network.

@@

@@

	Usually, a HSI dataset has labeled and unlabeled pixels.
	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
	and the rest of the labeled pixels was used to validate the model.
	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}

	\begin{figure}
		\begin{subfigure}
			\includegraphics{pic/p5/pc/1/img/trainMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}
			\includegraphics{pic/p5/pu/1/img/trainMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}
			\includegraphics{pic/p5/sl/1/img/trainMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}
			\includegraphics{pic/p5/sa/1/img/trainMap.eps}
			\caption{}
		\end{subfigure}
		\caption{Training set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
		\label{trainMaps}
	\end{figure}

	\begin{figure}
		\begin{subfigure}
			\includegraphics{pic/p5/pc/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}
			\includegraphics{pic/p5/pu/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}
			\includegraphics{pic/p5/sl/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\begin{subfigure}
			\includegraphics{pic/p5/sa/1/img/testMap.eps}
			\caption{}
		\end{subfigure}
		\caption{Validating set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
		\label{testMaps}
	\end{figure}
